---
title: "Lab04_Miko"
output: pdf_document
---
  


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Choose a candy characteristic and build a logistic regression model. Your model must include
3 covariates
Predict a different candy characteristic than the one we go over in class.
```{r}
#read the dataset


model = glm( chocolate~sugarpercent+pricepercent+hard, data=candy_data, family=binomial)
print(summary(model))


```

Explain what the coefficients mean in terms of log odds
Explain what the coefficients mean in terms of odds
Identify any covariates that are significant

1.Description of target variable and covariates
My model is trying to classify the candies by chocolate or not chocolate.
I chose 3 covariates: The percentage of sugar,vthe unit price percentile compared to the other candy, and whether or not the candy is hard candy.And I fit a logistic regression model to my candy data.

2.Description using log-odds
For log-odds, the intercept equals $-1.89 $, sugar percentile equals $-0.4205$, price percentile equals $4.3406$, and whether it is a hard candy equals $-2.5652$. Candy with a higher sugar percentile or as a hard candy is less likely to be chocolate (negative log-odds). However, candy that is more expensive indicates the candy is more likely to be chocolate flavor (positive log-odds).

3.Description using odds
For the odds, the intercept equals $e^{-1.89}=0.151$, sugar percentile equals $e^{-0.4205}=0.656$, price percentile equals $e^{4.3406}=76.753$, and whether it is a hard candy  equals $e^{-2.5652}=0.07$. A one unit decrease in the sugar percentile of a piece of candy results in a $0.6$ times increase in the the odds it is chocolate. A one unit increase in the price percentile results in a 77 times increase in the odds it is chocolate. If the candy is hard, it is less likely to also be chocolate.

Description of significant variables
The price percentile is a significant covariate. The pvalue <0.05 and indicates the estimated log-odds is unlikely to have come from a null distribution centered at a log-odds of $0$.
but the p value for sugar percentage is slightly larger than 0.05 but not significant enought to reject our null hypothesis that the coefficient of it is 0.


```{r}
#plot the model
colors = ifelse( candy_data$chocolate==1,'red','blue')
plot(candy_data$pricepercent,candy_data$sugarpercent,tck=0.02,col=colors)

coefficients = as.matrix(coef(model))
print(coefficients)

xs = seq(0,1,0.01)
lines(xs, (-coefficients[1]/coefficients[2]) - (coefficients[3]/coefficients[2])*xs)
```

```{r}
trainingData  = candy_data[,c('sugarpercent','pricepercent','hard')]
trainingData  = cbind(1,trainingData)

predictions   = as.matrix(trainingData) %*% coefficients
probabilities = exp(predictions)/(1+predictions)
decisions = ifelse(predictions>=0,1,0)

Accuracy = mean(candy_data$chocolate==decisions)
print(Accuracy)
```
Conclusion: Basically, we can guess correctly  about whether the candy is chocolate approximately 82% of the time by fitting a logistic regression model and including the sugar and price percentile, and whether the candy is hard.






