---
title: "Lab17"
author: "Kaiwen Lu & Evelyn Zhang"
date: "11/1/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Fork the 538 repository 
```{r}
d <- read.csv("./candy-data.csv")
d
```

# 2. Choose a candy characteristic and build a logistic regression model. 

```{r}
# 3 covariates are: chocolate, sugarpercent, bar
# Predict: hard | Is it a hard candy?
model <- glm(hard~chocolate+sugarpercent+bar, data=d, family=binomial)
summary(model)

```

# 3. Describe the coefficients corresponding to your covariates
# a) Explain what the coefficients mean in terms of log odds
# Ans: 
# chocolate: If the candy contains chocolate, the log odds that it is a hard candy decreases by 1.9862.
# sugarpercent: For a one unit increase in the candy's sugar percent, the log odds that it is a hard candy increases by 1.1533. 
# bar: If the candy is a bar, the log odds that it is a hard candy decreases by 16.9937.

# b)Explain what the coefficients mean in terms of odds
# Ans: 
# chocolate: If the candy contains chocolate, the odds that it is a hard candy decreases by e^1.9862 or roughly 7.3.
# sugarpercent: For a one unit increase in the candy's sugar percent, the odds that it is a hard candy increases by e^1.1533 or roughly 3.17. 
# bar: If the candy is a bar, the odds that it is a hard candy decreases by e^-16.9937 or almost 0.

# c)Identify any covariates that are significant
# Ans: No covariate is significant


# 4.Report the Accuracy of your logistic regression model
```{r}
trainingData  = d[,c('sugarpercent','chocolate','bar')]
trainingData  = cbind(1,trainingData)

coefficients = as.matrix(coef(model))
predictions   = as.matrix(trainingData) %*% coefficients
probabilities = exp(predictions)/(1+predictions)
decisions = ifelse(predictions>=0,1,0)

Accuracy = mean(d$hard==decisions)
print(Accuracy)
```
#We can make correct guesses about whether the candy is hard approximately 82% of the time by fitting a logistic regression model and including the sugar percentile, and whether the candy is chocolate or a bar.
